---
title: "Directed Acyclic Graphs"
author: "Sophia Wynona"
---

::: callout-note
Assignment V on Directed Acyclic Graphs - final submission
:::

# Task 1


```{r}
install.packages("ggdag")
install.packages("dplyr")
install.packages("ggplot2")
library(ggdag)
library(dplyr)
library(ggplot2)

# Your data
store_data <- data.frame(
  Store = c("A", "B", "C", "D"),
  y0 = c(135, 121, NA, NA),
  y1 = c(NA, NA, 102, 94),
  d = c(0, 0, 1, 1),
  y = c(135, 121, 102, 94),
  ITE = c(NA, NA ,NA ,NA)
)

# Create a DAG
dag <- dagify(y ~ d + y0 + y1,
              d ~ y0,
              y0 ~ ITE,
              y1 ~ ITE,
              exposure = "d",
              outcome = "y",
              latent = c("ITE"),
              coords = list(x = c(ITE = 1, y0 = 2, d = 3, y1 = 4, y = 5),
                            y = c(ITE = 2, y0 = 1, d = 2, y1 = 1, y = 2)))

# Plot the DAG
ggdag(dag) 


```

# Task 2
```{r}

# Load the data
data <- readRDS("C:/Users/sophi/OneDrive/Desktop/Causal Data Science for Business Analytics 2023/gitclone/cdsba-swynona/assets/Causal_Data_Science_Data/customer_sat.rds")

# View the structure of the data
str(data)

model1 <- lm(satisfaction ~ follow_ups, data = data)
summary(model1)

model2 <- lm(satisfaction ~ follow_ups + subscription, data = data)
summary(model2)

```

# Task 3 
Comparing coefficients and explanations : 

In Model 1, the coefficient for follow_ups is -3.3093. This suggests that for each additional follow-up call, the satisfaction decreases by 3.3093 units, assuming all other variables are held constant. This model does not account for the subscription variable.
In Model 2, the coefficient for follow_ups is 2.1944. This suggests that for each additional follow-up call, the satisfaction increases by 2.1944 units, when accounting for the subscription variable. This is a signifi cant change from Model 1, indicating that the subscription variable has a substantial impact on the relationship between follow_ups and satisfaction.
The coefficients for subscriptionPremium and subscriptionPremium+ are 44.7222 and 18.0722respectively. This suggests that the subscription level significantly affects customer satisfaction. Specifically, customers with a Premium subscription are, on average, 44.7222 units more satisfied than those with a Starter subscription, assuming all other variables are held constant. Similarly, customers with a Premium+ subscription are, on average, 18.0722 units more satisfied than those with a Starter subscription, assuming all other variables are held constant.
In conclusion, the subscription level appears to moderate the relationship between follow_upsand satisfaction. Without considering subscription, more follow-up calls are associated with lower satisfaction. However, when subscription is considered, more follow-up calls are associated with higher satisfaction. This could be because customers with higher-level subscriptions receive more benefits from follow-up calls, which increases their satisfaction. It’s also worth noting that customers with higher-level subscriptions are generally more satisfied.

# Task 4 - Plotting

```{r}
ggplot(data, aes(x = follow_ups, y = satisfaction)) +
  geom_point() +
  facet_wrap(~subscription) +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  labs(title = "Relationship between Follow-ups and Satisfaction",
       x = "Follow-ups",
       y = "Satisfaction")

```