---
title: "Difference-in-Differences"
author: "Sophia Wynona"
---

::: callout-note
Assignment VIII on Difference-in-Differences - final submission
:::


# Task 1
```{r}

data <- readRDS("C:/Users/sophi/OneDrive/Desktop/Causal Data Science for Business Analytics 2023/gitclone/cdsba-swynona/assets/Causal_Data_Science_Data/hospdd.rds")

library(dplyr)

# Assuming 'procedure' is a binary variable indicating whether the hospital introduced the new procedure and 'month' is a binary variable indicating before (0) and after (1) the introduction and 'satis' is the patient satisfaction score

mean_before_treatment <- data %>%
  filter(procedure == 1, month <= 6) %>%
  pull(satis) %>%
  mean()

mean_after_treatment <- data %>%
  filter(procedure == 1, month > 6) %>%
  pull(satis) %>%
  mean()

mean_before_control <- data %>%
  filter(procedure == 0, month <= 6) %>%
  pull(satis) %>%
  mean()

mean_after_control <- data %>%
  filter(procedure == 0, month > 6) %>%
  pull(satis) %>%
  mean()

```

# Task 2
```{r}


# Assuming 'hospital' is a factor variable indicating the hospital id and 'month' is a factor variable indicating the month of the survey

model1 <- lm(satis ~ procedure * month + month + hospital, data = data)
summary(model1)

model2 <- lm(satis ~ procedure * month + as.factor(month) + as.factor(hospital), data = data)
summary(model2)




```

Q : What's the difference between using month + hospital and as.factor(month) + as.factor(hospital) ?
A : The difference between month + hospital and as.factor(month) + as.factor(hospital) is that in the first case, month and hospital are treated as numeric variables, and the effect on satisfaction is assumed to be linear. In the second case, month and hospital are treated as factor variables, and the effect on satisfaction is not assumed to be linear but could be different for each level of the factor. This might be more appropriate if the effect of each month or each hospital on satisfaction is not necessarily linear.
