---
title: "Instrumental Variables"
author: "Sophia Wynona"
---

::: callout-note
Assignment IX on Instrumental Variables - final submission
:::

# Task 1
```{r}
install.packages('dagitty')
install.packages('estimatr')
install.packages('ggdag')
install.packages('ggplot2')
install.packages('dplyr')
library(dplyr)
library(ggplot2)
library(ggdag) 
library(estimatr)
library(dagitty)
data <- readRDS("C:/Users/sophi/OneDrive/Desktop/Causal Data Science for Business Analytics 2023/gitclone/cdsba-swynona/assets/Causal_Data_Science_Data/rand_enc.rds")
data

# Define the DAG
dag <- dagify(time_spent ~ used_ftr + rand_enc,
              used_ftr ~ rand_enc,
              exposure = "used_ftr",
              outcome = "time_spent")

ggdag(dag) + theme_dag()
```


# Task 2
Compute naive, biased estimate
```{r}
naive_model <- lm(time_spent ~ used_ftr, data = data)
summary(naive_model)
```


# Task 3
check assumption
```{r}
cor.test(data$rand_enc, data$used_ftr)

ggplot(data, aes(x = rand_enc, y = used_ftr)) +
  geom_point() +
  geom_smooth(method = "lm")
```

# Task 4
Compute IV estimate
```{r}
first_stage <- lm(used_ftr ~ rand_enc, data = data)
summary(first_stage)

pred_fs <- predict(first_stage)

pred_vs_actl <- tibble(
  pred = pred_fs,
  actl = data$used_ftr
)

ggplot(pred_vs_actl, aes(x = pred, y = actl, color = as.factor(actl))) +
  geom_jitter(alpha = .5) +
  scale_color_discrete(labels = c("Did not use feature", "Used feature")) +
  theme(legend.title = element_blank())

second_stage <- lm(data$time_spent ~ first_stage$fitted.values)
summary(second_stage)

model_iv <- iv_robust(time_spent ~ used_ftr | rand_enc, data = data)
summary(model_iv)

naive_estimate <- coef(summary(naive_model))["used_ftr", "Estimate"]
iv_estimate <- coef(summary(model_iv))["used_ftr", "Estimate"]

# Print comparison
cat("Naive Estimate: ", naive_estimate, "\n")
cat("IV Estimate: ", iv_estimate, "\n")






```

Q : is the native estimate biased ? Upward or downward ?

A : Yes, it appears that the naive estimate is biased. The naive estimate is 10.82269, while the Instrumental Variables (IV) estimate, which is generally considered less biased, is 9.738175.
Since the naive estimate is higher than the IV estimate, the naive estimate has an UPWARD bias. This means that the naive estimate overstates the true causal effect of the used_ftrvariable on time_spent. This bias could be due to the omission of the rand_enc variable in the naive model, which is accounted for in the IV model.
