---
title: "Regression Discontinuity"
author: "Sophia Wynona"
---

::: callout-note
Assignment X on Regression Discontinuity - final submission
:::

# Task 1
```{r}

library(dplyr)
library(ggplot2)
coupon <- readRDS("C:/Users/sophi/OneDrive/Desktop/Causal Data Science for Business Analytics 2023/gitclone/cdsba-swynona/assets/Causal_Data_Science_Data/coupon.rds")
shipping <- readRDS("C:/Users/sophi/OneDrive/Desktop/Causal Data Science for Business Analytics 2023/gitclone/cdsba-swynona/assets/Causal_Data_Science_Data/shipping.rds")


# Define bandwidths
half_bandwidth <- max(coupon$days_since_last_centered) / 2
double_bandwidth <- max(coupon$days_since_last_centered) * 2

# Filter data based on bandwidth
df_half <- coupon %>% filter(abs(days_since_last_centered) <= half_bandwidth)
df_double <- coupon %>% filter(abs(days_since_last_centered) <= double_bandwidth)

# Run regression analyses
model_half <- lm(purchase_after ~ days_since_last_centered + coupon, data = df_half)
model_double <- lm(purchase_after ~ days_since_last_centered + coupon, data = df_double)
```
half bandwidth model
```{r}
summary(model_half)
```

# Task 2
double bandwidth model
```{r}
summary(model_double)

```

# Task 3
Plotting to confirm arguments
```{r}

ggplot(shipping, aes(x=purchase_amount)) +
  geom_histogram(binwidth=1, fill="blue", color="black") +
  geom_vline(aes(xintercept=30), color="red", linetype="dashed", linewidth=1) +
  labs(title="Histogram of Purchase Amounts",
       x="Purchase Amount",
       y="Frequency",
       caption="Red line indicates the 30€ free shipping threshold") +
  theme_minimal()



```
Based on the histogram , it appears that the purchase_amount variable could potentially be used as a running variable with a cut-off at 30€. 
Reasons :
Cluster of Purchases: There is a significant number of purchases clustered around the 30€ mark. This could indicate that customers were motivated to increase their purchase amount to qualify for free shipping.
Threshold Effect: The red dashed vertical line at the 30€ mark on the x-axis indicates the free shipping threshold. If there is a significant difference in the distribution of the purchase amounts on either side of this line, it could suggest that the 30€ free shipping offer had an impact on customer behavior.
However, to confirm this argument, further statistical analysis is required. For instance, a regression discontinuity design could be used to estimate the causal effect of the free shipping offer on the purchase amount. This would involve fitting separate regression lines to the data on either side of the 30€ cut-off and then comparing the predicted values at the cut-off point.
